---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scpackages

<!-- badges: start -->
<!-- badges: end -->

The goal of scpackages is to ...

## Installation

You can install the released version of scpackages from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("scpackages")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("vondoRishi/scpackages")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(scpackages)
## basic example code
```

In this example we use the 10x data dowloaded from [here](https://support.10xgenomics.com/single-cell-gene-expression/datasets/2.1.0/neurons_900)

## Initialize and QC

First initialize and QC Seurat object with single command. This will also genarate QC plots

```{r warning=FALSE,fig.width=8,fig.height=6}
seurat_Obj <- read10XwithMarkergenes(
    tenxPath =  "/tmp/filtered_gene_bc_matrices/mm10/",
    pMin.cells = 3,
    pMin.features = 20,
    markerGenes = NULL,
    projectName = "1k_Brain_E18_Mm", 
    cellRangerAggregated = FALSE # If 10x data are aggrgated
)
```

## Filter

Now after inspecting the QC plots we want to keep good quality cells only. That can be done with following commands.

```{r filter,warning=FALSE,fig.width=8,fig.height=6}
seurat_Obj <- filterSeurat(seurat_Obj, 
                           mito.range = c(0, 5), # Cells with mitochondrial genes 0-5%
                           gene_range = c(1000,Inf) # Cells with more than 1000 genes 
                           )
```

## Report

The above commands can be run with different parameters or there could be several samples. It could be difficult to make separate markdown file for each object. Therefore we will use following command to genearate markdown notes about the above resuts and save "seurat_obj" for future use.

```{r report,message=FALSE,warning=FALSE,fig.width=8,fig.height=6}
report_QC(obj_scRNA = seurat_Obj,title = "1k_Brain_E18_Mm")
```

This will generate **1k_Brain_E18_Mm_currentDate.nb.html** report with all information and figures. Additionally, it will also save **seurat_Obj** as 1k_Brain_E18_Mm_currentDate.rds for future use.
