---
title: "Find unique clusterSolutions"
output: prettydoc::html_pretty
vignette: >
  %\VignetteIndexEntry{Find_uniq_clusterSolutions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup,message=FALSE,warning=FALSE}
library(scpackages)
```


## Load Seurat Object 

First we will load a scaled and normalized seurat object from disk.

```{r readSeurat,warning=FALSE,fig.width=8,fig.height=6}
scaled_cluster <- readRDS("../scaled_cluster.13_February_2020.rds")
```

## Gene ~ PC

Which genes are loaded in which principal component?

```{r gene_p,warning=FALSE,fig.width=8,fig.height=6}
tmp_hvf <-HVFInfo(scaled_cluster)
tmp_hvf$Symbol <- rownames(tmp_hvf)
# write.csv(tmp_hvf, file = "HVF_info.csv",row.names = FALSE)

## gene PCA Explore ##
scaled_cluster@misc$loading <- scpackages::pca_gene_loading(scaled_cluster)
scaled_cluster@misc$loading <-
  scaled_cluster@misc$loading %>% left_join(tmp_hvf, by = "Symbol")

library(ggrepel)

ggplot(scaled_cluster@misc$loading, 
       aes(x=factor(pca_fix),y=variance.standardized, label = Symbol)) +
  geom_point(color = ifelse(scaled_cluster@misc$loading$variance.standardized > 4 
                            , "red", "black")) +
  geom_text_repel(
    data = subset(scaled_cluster@misc$loading, variance.standardized > 6 )
  )+ggtitle(label = "Visualize the gene loading in each PCA ")
```

## Parameters

There are two parameters pca and resolution along with number of HVGs which controls number of cell types (cluster) 
### Elbow plot 

```{r param,warning=FALSE,fig.width=8,fig.height=6}

scaled_cluster@misc$elbowPlot+ggtitle("Where is the elbow")
## ??Where is the elbow does it matters ??
```

What are the optimal number of PC and resolution value?

```{r optimal_param,warning=FALSE,fig.width=8,fig.height=6}
featureRange <- seq(200,1000, by=400)
featureRange <- c(50,100)
pcRange <- seq(15,25,by = 5)
resolutionRange <- seq(0.4,1.2,by = 0.4)

scaled_cluster <- scpackages::gridFindClusters( Object = scaled_cluster, 
                                                pcRange, resolutionRange, featureRange,
                                                identPrefix = "solution", 
                                                verbose =FALSE)

ggplot(scaled_cluster@misc$data_NClust,
       aes(x = resolution, y = Cell_types, color=factor(feature) )) + geom_line() + facet_wrap(. ~ pc)
```

#### Keeping "PCA" constant, higher resolution provides higher number of cell types
#### Increasing number of PCA decreases max number of cell types

### With 17 PCA , resolution (0.4, 0.6,0.8) produces 6, 8 and 9 clusters  
### Are they belong to same solution?  
```{r vis_solution,warning=FALSE,fig.width=8,fig.height=6}
library(easyalluvial)
alluvial_wide(dplyr::select(
  scaled_cluster[[]],
  solution_17_0.4,
  solution_17_0.6,
  solution_17_0.8
)) + theme_bw()
```


## Cluster the similar solutions?

```{r group_clusters,warning=FALSE,fig.width=8,fig.height=6}
scaled_cluster <-  scpackages::findSimilarClusterSolution(scaled_cluster,
                                         identPrefix = "solution",
                                         similarityCut = 0.8)
plot(scaled_cluster@misc$cluster_G1, vertex.color = 
       rainbow(10, alpha = 0.8)[scaled_cluster@misc$clusterlouvain$membership])

```

## Look for same shape( number of cluster) with different color(solution) 


```{r warning=FALSE,fig.width=8,fig.height=6}
ggplot(  scaled_cluster@misc$meta_cluster,  aes(
                y = resolution,
                x = pca,
                # shape = factor(Cell_types),
                label = Cell_types,#membership,
                color = factor(membership)
              )
)  + geom_text()
#+  scale_color_manual(values =  rainbow(8)) #+  theme_dark()
```

#### Finding different solutions with same number of cell types.

```{r warning=FALSE,fig.width=8,fig.height=6}
cluster_representatives <- as_tibble( scaled_cluster@misc$meta_cluster %>% 
                                        group_by(membership,Cell_types) %>% 
                                        sample_n(1)) %>% arrange(pca,resolution)


x <- as.list(cluster_representatives %>% 
               filter( Cell_types==9 ) %>% 
               select(cluster_id))
alluvial_wide(scaled_cluster[[]][, as.character(x$cluster_id)]) + 
  theme(axis.text.x =  element_text(angle = 90)) +
  theme_bw() + 
  ggtitle(paste(    length(x$cluster_id),
    " different solutions with equal number of clusters"
  ))
```

Here, we can see there are 4 different clustering solutions although each of them give exact 9 cell types. For further discussion, **solution_15_0.8** is marked as reference set. Now the cell_types 3, 5, 6, 7 and 8 are always intact. Although, other cell_types are not constant in different solutions, but after subdividing into sub-group they remain **mostly** together.
