---
title: "Process Seurat Object"
output: prettydoc::html_pretty
vignette: >
  %\VignetteIndexEntry{CellCycle_cluster}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup,message=FALSE,warning=FALSE}
library(scpackages)
```


## Process Seurat Object for clustering

First we will load saved seurat object from disk.

```{r readSeurat,warning=FALSE,fig.width=8,fig.height=6}
seuratObj <- readRDS("/home/dasroy/data/Project/scpackages/1k_Brain_E18_Mm.12_February_2020.rds")
```


## 3-in-1
There are three steps need to do at first ; which are 

+ Normalization 
+ VariableFeatures (find variable genes) 
+ ScaleData  

These steps can be done by a single method with default values. It will also genarate **VariableFeaturePlot**. Only the variable features will be scaled as those are only required as input for PCA. 

**Note** We can pass any parameter of above "Seurat" functions to below function. 
Here in this example __nfeatures__ belongs to **VariableFeatures** .
```{r normScaleHVG,warning=FALSE,fig.width=8,fig.height=6}
seuratObj <- normScaleHVG(seuratObj,seuratVerbose = FALSE,nfeatures=1000)
```

To save the variance info of all the genes in a csv file. 
```{r hvg_info,eval=FALSE}
tmp_hvf <-HVFInfo(seuratObj)
tmp_hvf$Symbol <- rownames(tmp_hvf)
write.csv(tmp_hvf, file = "HVF_info.csv",row.names = FALSE)
```


## CellCycle 
Next we will check 
```{r CellCycle,message=FALSE,warning=FALSE,fig.width=8,fig.height=6}
library(readr)
cell_cycle_genes <- read_csv(system.file("extdata", "cell_cycle_genes.csv", package = "scpackages"))
cell_cycle_genes
```


**NOTE** cell_cycle_genes should have columns "Symbol" for gene names and "Phase" with values (S and M) for cell-cycle phases  

### Regression
At this step we will check 

+ Principal components(PC) are loaded with cell-cycle (CC) genes.
+ PCA plot with CC genes
+ regressing out CC effect with Seurat method **CellCycleScoring**
+ Again PCA plot with CC genes 

```{r CellCycle_regress,message=FALSE,warning=FALSE,fig.width=8,fig.height=6}
seuratObj <-qc_regress_CellCycle(seuratObj, cell_cycle_genes)
```


Plots will be saved in this following slots.

+ 'seuratObj@misc$CC_pca_bar'

+ 'seuratObj@misc$before_cc_pca'

+ 'seuratObj@misc$after_cc_pca'


## Cluster

### Elbowplot

```{r Elbowplot,message=FALSE,warning=FALSE,fig.width=8,fig.height=6}
seuratObj <- pcaProcess(seuratObj,features = VariableFeatures(seuratObj),jackStraw = FALSE)
# seuratObj@misc$elbowPlot
```

### Clustering
```{r Clustering,message=FALSE,warning=FALSE,fig.width=8,fig.height=6}
seuratObj <- makeClusterSeurat(seuratObj,maxDims = 20, res = 0.5)
# seuratObj@misc$umapPlot
```



### Cluster markers
```{r Clustering_markers,message=FALSE,warning=FALSE,fig.width=8,fig.height=6}
markers_info <-  FindAllMarkers( object = seuratObj,
                                 only.pos = TRUE, min.pct = 0.25,
                                 thresh.use = 0.25, verbose = FALSE )
head(markers_info)
seuratObj@misc$markers_info <- markers_info
```

To save the **markers_info** in a csv file. 
```{r echo=TRUE,eval=FALSE}
write.csv(markers_info, file = "cluster_markers.csv",row.names = FALSE)
```


#### Cell type information

Dummy cell type info. This data source must have two columns "Symbol" and "Gene_type"
```{r Dummy,message=FALSE,warning=FALSE,fig.width=8,fig.height=6}
marker_gene <- read_csv("/home/dasroy/data/Project/GeneExpression/scrna_workflow/marker_genes.csv")
marker_gene <- marker_gene[!duplicated(marker_gene$Symbol),]
head(marker_gene)
```

#### Annotation
```{r Annotation,message=FALSE,warning=FALSE,fig.width=8,fig.height=6}
library(dplyr)
markers_info <- left_join(markers_info,marker_gene, 
                          by = c("gene" = "Symbol")) %>% 
    replace_na(list(Gene_type = "Non skin"))

# Storing the info 
seuratObj@misc$markers_info <- markers_info

```


#### Rename clusters
```{r Rename,message=FALSE,warning=FALSE,fig.width=8,fig.height=6}
seuratObj <- renameCluster(ClusterInfo = markers_info, Object = seuratObj)
```

We used genes which should express in developing skin and hence all the clusters are marked with non-skin genes. The third field of the cluster names reflect the cluster sizes.

## Report 
It will genarate report and save seuratObj with filenames begining with **title** and ending with date_stamp.

```{r report,message=FALSE,warning=FALSE,fig.width=8,fig.height=6}
report_Cluster(obj_scRNA = seuratObj,title = "../scaled_cluster")
```

