---
output: 
  html_notebook: 
    fig_caption: yes
    toc: yes
    toc_float: true
date: "`r format(Sys.time(), '%d %B, %Y')`"    
params:
  set_title: "My Title!"
title: "`r paste(params$set_title)`"
---

```{css, echo=FALSE}
.scroll-100 {
  max-height: 400px;
  overflow-y: auto;
  background-color: inherit;
}
```

# Clustering 
## Highly variable features

```{r HVG,echo=FALSE}
obj_scRNA@misc$hvgPlot
```

<button class="btn btn-primary" data-toggle="collapse" data-target="#BlockName"> Show/Hide </button>  List of selected variable genes.
<div id="BlockName" class="collapse"  >  

```{r VariableFeatures,echo=FALSE,message=FALSE, class.output="scroll-100"}
x <- VariableFeatures(object = obj_scRNA)
print(x)
```

</div>   
   
## Cell cycle

### Loading on PC

Are principal component loaded with cell cycle genes?

```{r loadingPC,echo=FALSE}
obj_scRNA@misc$CC_pca_bar
```

#### Before regressing out
```{r before,echo=FALSE}
obj_scRNA@misc$before_cc_pca
```

#### After regressing out
```{r after_regress,echo=FALSE}
obj_scRNA@misc$after_cc_pca 
```

## Cluster

### Pca analysis
```{r elbow,echo=FALSE}
obj_scRNA@misc$elbowPlot
```

#### 0,0Max `r obj_scRNA@misc$maxPca` principal component and resolution `r obj_scRNA@misc$resolution` selected.

### Dimensional reduction

```{r dim_reduc,echo=FALSE}
obj_scRNA@misc$umapPlot
if(!is.null(obj_scRNA@misc$markers_info) ){
  DT::datatable(round_df(obj_scRNA@misc$markers_info,digits = 6), rownames = FALSE)
}else{
  print("Cluster markers are not found")
}
```

  
  
### Command History

<button class="btn btn-primary" data-toggle="collapse" data-target="#blockHis"> Show/Hide </button>  List of selected variable genes.
<div id="blockHis"  class="collapse">  
```{r history,echo=FALSE,message=FALSE,class.output="scroll-100"}
obj_scRNA@commands
```

</div>

### Session Info

<button class="btn btn-primary" data-toggle="collapse" data-target="#blockSesn"> Show/Hide </button>  List of selected variable genes.
<div id="blockSesn"  class="collapse">  
```{r sessn,echo=FALSE,message=FALSE,class.output="scroll-100"}
sessionInfo()
```

</div>
